\documentclass[]{Vishnu-Resume}


\begin{document}

\lastupdated

\namesection{Vishnu}{Srivastava}{\href{https://www.linkedin.com/in/zxingz/}{ \urlstyle{same}\url{https://www.linkedin.com/in/zxingz/}} \\
\href{mailto:vishnu-srivastava@hotmail.com}{vishnu-srivastava@hotmail.com} | \href{tel:+919990063640}{Tel: +91 9990063640}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Waterloo}
\descript{\href{https://uwspace.uwaterloo.ca/handle/10012/11732}{MMath Thesis in Computer Science}}
Major: Software Engineering \\
Guide: \href{https://cs.uwaterloo.ca/about/people/palencar}{Prof. Paulo Alencar}\\
\location{Waterloo, ON | CGPA : 87\% \\ Sep'14 - May'17}

\sectionsep
\sectionsep
\sectionsep
\subsection{Delhi Technological}
\subsection{University}
\descript{B.Tech Engineering Physics}
Major:  Robotics \& Info Systems \\
\location{New Delhi, India \\ May'09 - May'13}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Website:// \href{https://vishnu.the-software.dev}{\custombold{www.the-software.dev}} \\
Github:// \href{https://github.com/zxingz}{\custombold{github.com/zxingz}} \\
LinkedIn://  \href{https://www.linkedin.com/in/zxingz/}{\custombold{linkedin.com/in/zxingz}} \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Python \textbullet{} Java \textbullet{} C++/C  \textbullet{} JavaScript \textbullet{} Bash
\sectionsep

\subsection{Python}
Apache Airflow \textbullet{} Pandas \textbullet{} PySpark  \textbullet{} Django \textbullet{} PyTorch  \textbullet{} Spacy   \textbullet{} SQLAlchemy  \textbullet{} Scikit-Learn \textbullet{} Flask
\sectionsep

\subsection{JavaScript}
Bootstrap4 \textbullet{} jQuery \textbullet{} ReactDOM 
\sectionsep

\subsection{Data Visualization}
Power BI \textbullet{} Tableau \textbullet{} Grafana \textbullet{} D3.js  \textbullet{} Plotly \textbullet{} Kibana \textbullet{} Dash \textbullet{} Metabase
\sectionsep

\subsection{DB/Cache/QL}
 Postgresql  \textbullet{} Redis  \textbullet{} Hive  \textbullet{} MySQL  \textbullet{} Oracle  \textbullet{} Hbase  \textbullet{} Trino(Presto)
\sectionsep

\subsection{Dev/CI/CD}
Jenkins \textbullet{} Docker \textbullet{} Git \textbullet{} SVN
\sectionsep


\subsection{Monitoring}
ElasticSearch \textbullet{} Filebeat \textbullet{} CAdvisor
\sectionsep

\subsection{Environments}
Linux \textbullet{} Windows  \textbullet{} Hadoop \textbullet{} Apache Mesos-DC/OS

\subsection{Cloud}
GCP-BigQuery \textbullet{} S3(Minio) \textbullet{} DataProc(Spark)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience: 9+ Years}
%\descript{Industry Experience: 5 years 8 months}
%\descript{Research Experience: 2 years 8 months}
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\runsubsection{Adobe}
\descript{}
\descript{Sr. Data Science Analyst(Business Intelligence Engineer) | AdTech}
\location{September 2021 – Present | Noida, India}
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\sectionsep
\begin{tightemize}
%\item Managing a team of 3 Analysts.
\item Working on generating impressions and conversions reports using identity graph and predictive analytics from LiveRamp and pixel conversion logs and ingesting in Power BI.
\item Running jobs on AWS Data Pipeline and AWS EMR for realtime data Visualization and Ad Campaign Optimization.
\end{tightemize}
\sectionsep
\sectionsep
\sectionsep
\runsubsection{Scotiabank (Canada)}
\descript{}
\descript{Data Scientist-Manager | International Banking Analytics}
\location{August 2019 – September 2021 | Toronto, ON}
\begin{tightemize}
\item Developed pricing simulation dashboard for Caribbean operations to simulate changes in fee structures.
\item Worked on customer churn model and mortgage rate estimation for CCAU region.
\item Manage analytics pipeline to Scotiabank's Latin America and Caribbean businesses.
\end{tightemize}
\#\custombold{Microservices}  \#\custombold{Spark} \#\custombold{APIs}  \#\custombold{Data Visualization}
\sectionsep

\descript{Data Scientist | decision sciences}
\location{July 2018 – August 2019 | Toronto, ON}
\begin{tightemize}
\item Used Grafana and Postgres to create dashboards for Electronic Money Transfer transactions.
\item Analyze Electronic Money Transfers using PySpark to gather transaction information(Email ID, Acc No., IP) from log files on HDFS.
\item Developed Reading Comprehension System using Google Research's BERT model for SEDAR News documents.
\end{tightemize}
\sectionsep

\descript{Programmer Analyst | Centralized Risk Platform}
\location{July 2017 – July 2018 | Toronto, ON}
\begin{tightemize}
\item Deployed Apache Airflow, Elasticsearch, Filebeat and monitoring stack (Prometheus, Grafana, CAdvisor, NodeExporter).
\end{tightemize}
\sectionsep

\runsubsection{University of Waterloo}
\descript{| Research Assistant}
\location{September 2014 – May 2017 | Waterloo, ON}
\begin{tightemize}
\item Research on {\href{https://uwspace.uwaterloo.ca/handle/10012/11732}{"Multi-Agent Modeling of Risk-Aware and Privacy-Preserving Recommender Systems"}}.
\end{tightemize}
\sectionsep

\runsubsection{ERNST \& YOUNG L.L.P}
\descript{| Associate Consultant | IT Advisory}
\location{June 2013 – July 2014 | New Delhi, India}
\begin{tightemize}
\item Develop \& Design UI and Logic using SAP Advanced Business Application
Programming. Customize and Develop Data Report and Form Generation.
\end{tightemize}
\sectionsep

\runsubsection{SAMSUNG R\&D LAB}
\descript{| Intern | Data Analytics Group}
\location{May 2013 – June 2013 | New Delhi, India}
\begin{tightemize}
\item Extraction of movie trailer links from MovieLens data sets. UI for Samsung Smart TV gesture recognition Application.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Portfolio
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\textbullet{} \href{https://github.com/zxingz/WebApp}{The-Software.Dev} \textbullet{} \href{https://github.com/zxingz/Workflow}{Airflow} \textbullet{} \href{https://github.com/zxingz/Monitoring}{Monitoring} \textbullet{} \href{https://github.com/zxingz/machine_comprehension}{Machine Comprehension- Google BERT}  \textbullet{} \href{https://github.com/zxingz/trader}{High Frequency Trading}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\end{document}